A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-12 Header.Rmd
図・アブストを修正など 3102 words。 ラストの確認をしてRM・KFにパスかな。

output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: TRUE
fontsize: 20pt
geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  # word_document:
  #   toc: FALSE
  #   fig_caption: TRUE
---

@@

evalFig <- T
base_size <- 20
Annotate_size <- 6

@@

  The spectral photon flux density distribution (SPD) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~) but also interacts on it.
  A plausible mechanisms of the interaction, some situations in which the interaction should be concerned, and the selection of appropriate measuring light for evaluation of photosynthesis are summarized.
  *P*~n~ should be measured under *in situ* conditions depending on the purpose of the study.
  In prospective studies focusing on plant growth after the measurements, the measurements should be made under the SPD of light that the plant will be subject to.
  In retrospective studies aiming to elucidate causes of differences between the experimental groups, the measurements should be made under the SPDs of light that the plants have received during the treatments.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to comprehend general photosynthetic characteristics of the leaves.
  *P*~n~ under a single-pattern SPD of measuring light is only an aspect of the photosynthetic characteristics of the leaf.
  The obtained result must be discussed in connection with the SPD of measuring light so as not to make biased evaluation caused by the interaction.

>>>>

output:
#   pdf_document:
#     latex_engine: xelatex
#     fig_caption: TRUE
# fontsize: 20pt
# geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  word_document:
    toc: FALSE
    fig_caption: TRUE
---

@@

evalFig <- T
base_size <- 20
Annotate_size <- 5

@@

  The spectral photon flux density distributions (SPDs) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also interacts on it.
  This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
  The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
  For studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
  In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
  The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.

### 2016-08-12 Main.Rmd
図・アブストを修正など 3102 words。 ラストの確認をしてRM・KFにパスかな。

  The effect of the SPD of growth light on *P*~n~ depends on the SPD of the measuring light.
  In other words, the interaction between the SPDs of the growth light and the measuring light affect the *P*~n~ of a leaf.
  In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
  We then suggest situations in which the interaction should be particularly considered.
  We also discuss good practice for selecting measuring light with an appropriate SPD for *P*~n~ measurements.
  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the SPD of measuring light.
  Although these subjects are not discussed in this article, several cited articles are available for these topics.

@@

  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 2).
  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amoutn of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
  This shortage in the EED to PSI limits the ETR, thereby leading to lwoer photochemical quantum yield of PSII (Fig. 2C).
  When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
  In both cases, the excess energy is dissipated mainly as heat and fluorescence.
  Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
  Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
  The stoichiometry appears to adjust to the SPD of the growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  These adjustments in the EED properties might help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
  As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of the growth light.
  **PSII-light PSI-light が使われることがある**.
  The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
  For instance, the SPD of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by state transitions, the long-term adjustments in the EED properties are thought to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

@@

  These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of the growth light.
  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under a measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of light, the results will inevitably be biased depending on the SPD of the measuring light.

@@

  Several studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Growth light provided by most artificial light sources contains little FR light.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
  This is because FR light is hardly ‘photosynthetically active’ and promotes excessive stem elongation.
  However, several recent papers have suggested the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light are more similar to PSI-leaves in terms of their EED properties, compared with leaves of plants grown without supplemental FR light.
  Therefore, comparing the *P*~n~ of leaves of plants grown with and without supplemental FR light using BR-light as the measuring light might lead to a biased evaluation because of the interaction, as demonstrated in our recent report [@Murakami_et_al2016PP].

@@

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g. @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
  However, the measurements under sunlight may be less reliable because of fluctations in the incident PPFD.
  In such cases, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure the reproducibility and reliability of the results.
  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.

>>>>

  The effect of the SPD of growth light on *P*~n~ depends on the SPD of measuring light.
  In other words, the interaction between the SPDs of growth light and measuring light affect the *P*~n~ of a leaf.
  In this short article, we describe a plausible mechanism for this interaction, based on the excitation energy distribution balance between the photosystems.
  We then suggest situations in which the interaction should be particularly considered.
  We also discuss good practice for selecting measuring light with an appropriate SPD for *P*~n~ measurements.
  Several mechanisms other than the excitation balance, such as stomatal responses [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and vertical PFD profile within a leaf [@Terashima_et_al2009PCP] affect photosynthesis via the SPD of measuring light.
  Although these subjects are not discussed in this article, several cited articles are available for these topics.

@@

  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 2).
  When there is excess excitation energy at PSII (i.e. under PSII-light), the smaller amount of excitation energy distributed to PSI results in lower photochemical reaction rates at PSI than at PSII.
  This shortage in the EED to PSI limits the ETR, thereby leading to lower photochemical quantum yield of PSII and balaced ETR between PSII and PSI (Fig. 2C).
  When PSI absorbs excess excitation energy (i.e. under PSI-light), the excitation energy distributed to PSII limits the ETR and lowers the yield of PSI (Fig. 2B).
  In both cases, the excess energy is dissipated mainly as heat and fluorescence.
  Consequently, the entire photosynthetic quantum yield---ETR per absorbed photons by the leaf---becomes smaller.
  Therefore, balancing the EED between PSII and PSI is essential for plants to retain a high photosynthetic quantum yield.
  Imbalanced excitation between the photosystems is supposed to damage leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].

  Apparently, the EED at a given SPD of light is also affected by the composition of the thylakoid components, especially the stoichiometry between PSII and PSI.
  The stoichiometry appears to adjust to the SPD of the growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  These adjustments in the EED properties might help the leaves to maintain a high photosynthetic quantum yield under different growth lights [@Chow_et_al1990PNAS].
  As a result of these adjustments in the EED properties of a leaf, the spectrum of excitation balance (Fig. 1) differs depending on the SPD of the growth light.
  The categories of light, that is, ‘PSII-light’ and ‘PSI-light’, are defined for a given leaf on a relative scale, not an absolute scale.
  For instance, the SPD of light that is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 2A), can overexcite PSII in PSI-light-grown leaves (Fig. 2C).
  Therefore, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complexes of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be compensated for by state transitions, the long-term adjustments in the EED properties are thought to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

@@

  These reports suggested that the EED properties of a leaf might be tuned to the PSII/PSI-biased level of growth light.
  It is expected that a leaf will perform a higher ETR per absorbed photons by the leaf under measuring light with a PSII/PSI-biased level similar to that of the growth light (Fig. 3).
  When leaves grown under different SPDs of light are compared and evaluated under a specific SPD of measuring light, the results will inevitably be biased depending on the SPD of the measuring light.

@@

  Several studies published over the last decade have investigated the effects of the SPD of the growth light on plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Hogewoning_et_al2012PC; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Growth light provided by most artificial light sources contains little FR light.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs used for assimilation lighting all emit typical PSII-light (Fig. 4).
  This is because FR light is hardly ‘photosynthetically active’ and promotes excessive stem elongation.
  However, several recent papers have suggested the significance of supplemental FR light on plant growth and development [for a review, see @Demotes-Mainard_et_al2016EEB].
  Since FR light overexcites PSI, leaves grown under PSII-light with supplemental FR light are more similar to PSI-leaves in terms of their EED properties, compared with leaves of plants grown without supplemental FR light.
  Therefore, comparing the *P*~n~ of leaves of plants grown with and without supplemental FR light using BR-light as the measuring light might lead to a biased evaluation because of the interaction, as demonstrated in our recent report [@Murakami_et_al2016PP].

@@

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g. @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
  However, the measurements under sunlight may be less reliable because of fluctations in the incident PPFD.
  In such cases, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.
  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.
